---
format: gfm
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# broom.asreml

<!-- badges: start -->

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The `broom.asreml` provides tidy format for extracting model components for asreml objects.

## Installation

You can install the development version of broom.asreml from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("emitanaka/broom.asreml")
```

## Example

```{r}
#| message: false
#| output: false
library(asreml)
library(broom.asreml)
fit <- asreml(yield ~ Variety, 
              random = ~Column + Row, 
              data = wheat)
```

## Single row summary of model

```{r}
glance(fit)
```

## Tidy model parameters


### Fixed effects (E-BLUEs)

```{r}
tidy(fit, "fixed")
```

### Random effects (E-BLUPs)

```{r}
tidy(fit, "random")
```

### Variance components (REML estimates)

```{r}
tidy(fit, "vcomp")
```

### Wald test 

```{r}
tidy(fit, "wald")
```

## Augment data with model information

```{r}
augment(fit)
```




